Modelling Mass Migration based on Spatial\\ Generative Agent-Based Trade Simulation

### 2017-05-28 paper/paper.tex
Added results and discussion sections and updated citations

%All authors should be included in the submission. To anonymise the submission, set to 'true' the \reviewcopy command below. However, before submitting  you can check that all the informations you entered are correct by temporarily setting it to 'false'. Please remember to set it back to 'true' before the submission.
\reviewcopy{false}

@@

Private variables:
\begin{description*}
	\item[Resources:]
		Variable ranging from 0 to (potentially) infinity. This represents how much an agent possesses and influences his trading behaviour.

@@

Static variables:
\begin{description*}
	\item[willingness-to-trade-factor ($\wtf$):]
		Percentage representing the chance that an agent actually makes a trade with someone else, independently of all the other factors.

@@

	social behaviour:
	\begin{description*}
		\item[$\boldsymbol{\gdf}$:]
			The biggest part of our agent's characters is decided by the value of the gold-dig-factor (cf. gold-dig-factor in the section Entities, state variables and scales). The idea behind this is that a $\gdf$ of 1 causes behaviour similar to socialist/communist ideas while a $\gdf$ of 0 leads to phenomena similar to capitalism. Capitalism favours accumulation of money, be it in the hands of individuals or corporations \citep{marx}. On the other side of the spectrum socialism favours the equal distribution of money as can be seen in socialist ideas such as progressive taxes \citep{moyes}. We mirror this using the $\gdf$ in the following way: an agent with a high $\gdf$ will, when considering all agents that have proposed him a trade, favour the agent with the least resources over any other agent, no matter how much sympathy he has for any of them. It is obvious that this favours the equal distribution of resources since in a scenario of unequally distributed wealth with all agents having a $\gdf$ of 1 all poor agents will propose trades to (really it's requesting resources from) rich agents which, in turn will accept these trades without consideration. On the other hand a $\gdf$ close to zero will favour the emergence of groups of agents which will exclusively help other agents of the group. Poor agents requesting resources will lose the sympathy of richer agents because requesting resources will lead to a decrease of the sympathy factor while rich agents who don't have to request resources very often will maintain a high sympathy factor.

@@

	structure:
	\begin{description*}
		\item[Logical Connections:]
			The agents and the edges between them form a graph or a network. When there exists an edge between two agents it means that they "know" each other and that they are able to trade with each other. In this sense the network really captures the meaning of a social network, especially as we assume that all social interaction is trade. As shortly mentioned above the connection between two agents also acts as an implicit channel of information between them: an agent receiving a trade request from one of his neighbours learns something about this agent's situation and, as the situation of an agent mostly depends on his position on the map, also about the surrounding world. A well connected agent is thus better informed than others and is thus more likely to be able to adopt his position (cf: movement) better than others.

@@

>>>>

%All authors should be included in the submission. To anonymise the submission, set to 'true' the \reviewcopy command below. However, before submitting  you can check that all the informations you entered are correct by temporarily setting it to 'false'. Please remember to set it back to 'true' before the submission.
\reviewcopy{true}

@@

\textbf{\underline{Private variables}}:
\begin{description*}
	\item[Resources:]
		Variable ranging from 0 to (potentially) infinity. This represents how much an agent possesses and influences his trading behaviour.

@@

\textbf{\underline{Static variables}}:
\begin{description*}
	\item[willingness-to-trade-factor ($\wtf$):]
		Percentage representing the chance that an agent actually makes a trade with someone else, independently of all the other factors.

@@

	\textbf{\underline{Social behaviour}}:
	\begin{description*}
		\item[$\boldsymbol{\gdf}$:]
			The biggest part of our agent's characters is decided by the value of the gold-dig-factor (cf. gold-dig-factor in the section Entities, state variables and scales). The idea behind this is that a $\gdf$ of 1 causes behaviour similar to socialist/communist ideas while a $\gdf$ of 0 leads to phenomena similar to capitalism. Capitalism favours accumulation of money, be it in the hands of individuals or corporations \citep{marx}. On the other side of the spectrum socialism favours the equal distribution of money as can be seen in socialist ideas such as progressive taxes \citep{moyes}. We mirror this using the $\gdf$ in the following way: an agent with a high $\gdf$ will, when considering all agents that have proposed him a trade, favour the agent with the least resources over any other agent, no matter how much sympathy he has for any of them. It is obvious that this favours the equal distribution of resources since in a scenario of unequally distributed wealth with all agents having a $\gdf$ of 1 all poor agents will propose trades to (really it's requesting resources from) rich agents which, in turn will accept these trades without consideration. On the other hand a $\gdf$ close to zero will favour the emergence of groups of agents which will exclusively help other agents of the group. Poor agents requesting resources will lose the sympathy of richer agents because requesting resources will lead to a decrease of the sympathy factor while rich agents who don't have to request resources very often will maintain a high sympathy factor.

@@

	\textbf{\underline{Structure}}:
	\begin{description*}
		\item[Logical Connections:]
			The agents and the edges between them form a graph or a network. When there exists an edge between two agents it means that they "know" each other and that they are able to trade with each other. In this sense the network really captures the meaning of a social network, especially as we assume that all social interaction is trade. As shortly mentioned above the connection between two agents also acts as an implicit channel of information between them: an agent receiving a trade request from one of his neighbours learns something about this agent's situation and, as the situation of an agent mostly depends on his position on the map, also about the surrounding world. A well connected agent is thus better informed than others and is thus more likely to be able to adopt his position (cf: movement) better than others.

@@

\section{Results}
We succeeded in building a system which is highly adaptive despite being based solely on very simple rules. Running it with many different distribution functions we learned that the agents will always distribute themselves in a beneficial way. Even under very hard circumstances where the distribution function cuts off all agents from good soil they managed to get back on that good soil due to some random movement. Coming back to our initial question we found that the connectedness of an agent which allows him to propose trades and a certain social preference of its neighbours which will enable money and information flow are crucial for its success. To quantify these findings we've seen that GDF of 1 and WTF of 1 alongside medium connectedness leads to the best results, meaning longest survival and highest adaptivity of the agents. We conclude that in a system with these assumptions very "social" agents (social in the same spirit as described in the section on design principles) are best suited for survival. Preference for itself or for "friends" can only harm the adaptivity of the system as there is a one-to-one correspondence between the number and distribution of an agent's neighbours and this agent's adaptivity and thus its success.

\section{Discussion}
Despite the abstract nature of this model it nevertheless allows us to draw positive, as well as normative conclusions which we will illustrate in the following.
The cause and process of migration in our model coincides on many levels with theories trying to explain migration. Two ways in which migration is understood are neoclassical economics and relative deprivation theory \citep{jennissen}. Migration from the perspective of neoclassical economics is a problem of demand and supply: Having lower wages in one place and higher wages in another place indicates that the first one has a surplus of labour and a shortage of money while the latter is directly opposite. People moving from the regions with lower wages to the regions with higher wages are, from a neoclassical economical perspective, the logical consequence. We can observe exactly this behaviour in our model: first we check that our agents fulfill the three assumptions of neoclassical economics \citep{weintraub}. Our agents have rational preferences in the form of GDF and WTF and they maximize utility; both of these assumptions have already been broadly explained in the section on design choices. Other than that our agents also decide everything on the basis of full and relevant information, this together with the flow of information in our model has also been discussed in said section. We therefore can conclude that our agents are well-suited for a neoclassical model. Running the model with a realistic distribution function we observe that some time after the random initial distribution of the agents an equilibrium is reached where agents are distributed around the areas of high prosperity; the market has reached an equilibrium.
Relative deprivation theory on the other hand explains migration from another perspective. Instead of viewing the system from a bird's eye perspective it looks at the individuals. Richard Schaefer defines relative deprivation in the following way: "the conscious experience of a negative discrepancy between legitimate expectations and present actualities." \citep{schaefer}. We can easily see that this is what happens in our model if we take a less bird's-eye-like perspective: agents learn that their neighbours fare better than themselves and thus want to improve their own position.
Our model takes overpopulation of certain areas into consideration as resources are always distributed per parcel and all agents on a parcel share the resources it yields. We found that building mechanisms into our model that allow an agent to compare its current position to the position in the last tick vastly improved the longevity of the agents as it reduces overpopulation of certain areas. In the real world we often observe the bad impacts rural flight has on the fleeing people as many find their situation actually worsened compared to before \citep{weeks}. One problem is that big bursts of rural flight lead to an increase in population which can not be dealt with by the existing infrastructure \citep{harris}. This is very similar to the effect in our model before our amelioration. Our model therefore suggests that enabling higher mobility of migrants could lead to better results.

Most of our observations based on running the simulation and observing the behaviour. Another approach would be to actually let the agents learn the best initial configurations. This would provide better ground for answering the question of what kind of society works best in this model.
